---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pvcalibrater

<!-- badges: start -->
```{r, echo = FALSE}                                                                                                       
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])                                                                 
version <- gsub('-', '.', version)                                                                                          
```                                                                                                                         
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

pvcalibrater calibrates agent-based-model for solar photo-voltaic adoption by Irish households. 

## Installation

You can install pvcalibrater from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Phalacrocorax-gaimardi/pvcalibrater")
```

## Data

The PV survey dataset __pv_data__ has 27 discrete features of 1208 agents. The survey questions and the corresponding answer choices are described in __pv_qanda__. Samples from __pv_qanda__ and __pv_data__ are given below.

```{r data, echo = F}
library(pvcalibrater)
library(knitr) %>% suppressWarnings()
## survey answers
kable(pv_qanda[30:37,],row.names=F)
## the data
kable(pv_data[10:14,],row.names=F)
##restrict to owner-occupiers excluding apartments
```

Subsets of the full survey can be used to train alternative models. For example, _pv_data_oo_ excludes non owner-occupiers and apartments 

```{r data2, echo = T}
pv_data_oo <- pv_data %>% dplyr::filter(q1 %in% 2:4,q3 %in% 1:2)
```

## Model

Firstly, __pv_calibrater__ converts stated adoption likelihood (Likert scores __qsp22_7__) to adoption utilities, using simple assumptions for utility uncertainty and hypothetical bias. Hypothetical bias is fined-tuned later in the ABM by matching the observed PV adoption. Secondly, __pv_calibrater__ generates an additive boosted tree regression model trained on the utilities. The model predicts an agent's expected adoption utility as a function of the discrete values taken by 26 agent features.

```{r eval=F}
##xgboost
bst <- get_boosted_tree_model(pv_data_oo,complexity_factor = 1.5)
```

All features contribute to the model adoption utility of an agent. These contributions are identified as Shapley importance scores.

```{r eval=F}
##partial utility contribution for each feature and agent
shap_scores_long_sample <- get_shap_scores(pv_data_oo,bst)
```

An ABM abstracts out some features that vary over the simulation time. --pv_calibrater__ assumes these are financial and social. Averaging over all agents gives the empirical financial and social partial utility functions. The remaiing features have an average value $\theta$ (barrier term)

```{r eval=T}
##mean partial utility functions for features used in ABM (financial q9_1, social qsp21 and barrier)
get_empirical_partial_utilities(shap_scores_long_sample)
```

An individual agents adoption utility is a sum of the mean partial utilities with weights:

```{r eval=T}
##individual weights for financial, social and barrier terms
get_model_weights(shap_scores_long_sample)
```


## Plots

The social influence contribution to adoption utility

```{r plot1, echo = T}
plot_feature_utility(shap_scores_long_sample, "qsp21")
```

A pairs plot showing the distribution of weights is created by plot_weights

```{r plot2, echo = T}
plot_weights(shap_scores_long_sample)
```

